Draft of Paper for SER - 574

### 2019-01-20 Draft/Parts/Main.tex
Added main section

>>>>

\section{Importance of Architecture/Design}
\label{sec:imp_of_dsgn}
As we know that the product owner in an agile process model is the person with the vision of what the project will look like and if it is a small team the product owner can clearly pass this to each and every member of the team and even each member can query the product owner directly when in doubt. But in large scale projects where multiple agile teams are working together in supervision of a few product owners it is practically impossible for the owner to keep doing what they did in a small team, that’s where a formal definition of their vision comes in handy as it enables the teams to look up to something when encountering a design decision. The design or architecture in this case acts as a common vision for not only the teams but also for the communication between all the product owners. The design acts as a “deadlock breaker in decisions” \cite{architecureRole_article} as when the teams can’t come to a common consensus the design shows the path to take.
